### 2023-07-17 supplement.qmd
Download data with R

@@

```{r}
#| label: data-read
#| message: false

@@

```{r}
#| label: clean-sessions
#| code-fold: show
#| include: true

@@

# Count of data with all wellbeing observations
dat_total_wellbeing <- dat |> 
  summarise(
    n_total = n(),
    n_players = length(unique(pid))
  )

dat <- dat |> 
  mutate(
    session_has_pre = duration[1] == 0,
    session_has_post = sum(!is.na(mood)) > 1,
    .by = c(pid, session)
  )

dat |> 
  count(session_has_pre, session_has_post) |> 
  mutate(p = n / sum(n))

dat <- dat |> 
  filter(session_has_pre, session_has_post) |> 
  select(!contains("_has_"))
```

```{r}
bind_rows(
  "Total" = dat_total_wellbeing,
  "This study" = dat |> 
    summarise(
      n_total = n(),
      n_players = length(unique(pid))
    ),
  .id = "Data"
)
```

@@

Here is a scatterplot of the raw trimmed data.

>>>>

## Download data

We download data from the main PWS dataset repo:

```{r}
#| label: data-download
path <- "data-raw/data.zip"
if (!file.exists(path)) {
  download.file("https://osf.io/download/j48qf/", destfile = "data-raw/data.zip")
  dir.create("data", FALSE)
  unzip(path, files = c("data/demographics.csv", "data/study_prompt_answered.csv"))
}
```

@@

```{r}
#| label: data-read
#| code-fold: show
#| message: false

@@

```{r}
#| label: sessions-create
#| code-fold: show

@@

# Count of data with all wellbeing observations
dat_total <- dat |> 
  summarise(
    n_total = n(),
    n_players = length(unique(pid))
  )

# Include only sessions with "pre-" and "post" measure(s)
dat <- dat |> 
  filter(
    # Session has a wellbeing measure at time = 0
    duration[1] == 0, 
    # Session has at least two non-missing wellbeing measures (e.g. pre + 1 post)
    sum(!is.na(mood)) > 1,
    .by = c(pid, session)
  )

# Count of data to be used in these analyses  
dat_filtered <- dat |> 
  summarise(
    n_total = n(),
    n_players = length(unique(pid))
  )

# Summary
bind_rows(
  "total" = dat_total,
  "filtered" = dat_filtered,
  .id = "Data"
)
```

@@

Here is a scatterplot of the raw data
